### 2021-10-06 analysis/analyse_proportion_of_scouts.Rmd
changed axis around for lm exploratory plots

rural_lu_long %>%
  ggplot(aes(x = p, y = values)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~landuse, ncol = 2) +
  theme(
    text = element_text(size = 8)
  )
```

@@

urban_lu_long %>%
  ggplot(aes(x = p, y = values)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~landuse, ncol = 2) +
  theme(
    text = element_text(size = 8)
  )

>>>>

rural_lu_long %>%
  ggplot(aes(x = values, y = p)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~landuse, ncol = 2, scales="free") +
  theme(
    text = element_text(size = 8)
  )
```

@@

urban_lu_long %>%
  ggplot(aes(x = values, y = p)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(~landuse, ncol = 2, scales="free") +
  theme(
    text = element_text(size = 8)
  )
